---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(123)
```

# hypogeom

<!-- badges: start -->
<!-- badges: end -->

`hypogeom` implements the basic distribution functions for the hypogeometric distribution, which is the sum of independent geometric distributions.
It is the discrete analogue of the hypoexponential distribution.

## Installation

You can install the development version of from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("damian-t-p/hypogeom")
```

## Example

This package contains functions that are typically associated with probability distributions in R.
That is, the probability mass function, distribution function, quantile function, and random generator.

```{r example}
library(hypogeom)

# The hypogeometric distribution is parameterised by a vector of success probabilites,
# which are the parameters of the constituent geometric distributions
probs <- c(0.2, 0.5, 0.1)

dhypogeom(c(0, 1, 2, 10), probs)
```

```{r}
phypogeom(c(-1, 2, 5.5), probs)
```

```{r}
qhypogeom(c(0.05, 0.5, 0.95), probs)
```

```{r}
rhypogeom(10, probs)
```
